---
title: "Hover by Click"
author: "Micah Daley-Harris"
date: "3/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(magrittr)
require(plotly)
require(htmlwidgets)
```


```{r cars}

htmltools::div(id = "myDiv",
plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, hovertext = ~Species, name = "A") %>% add_markers() %>% layout(hovermode = "closest", dragmode = F) %>%
  onRender("
function(el, x) {
  el.on('plotly_click', function(data){
    hoverInfo = document.getElementById('hoverinfo');
    var pts = data.points[0].hovertext + '.mp4';
    hoverInfo.innerHTML = pts
  });
}")
)

htmltools::div(id = "theDiv")
htmltools::div(id = "hoverinfo", "my old text")

```


<script>
var myPlot = document.getElementById('myDiv'),
    hoverInfo = document.getElementById('hoverinfo'),
    d3 = Plotly.d3,
    N = 16,
    x = d3.range(N),
    y1 = d3.range(N).map( d3.random.normal() ),
    y2 = d3.range(N).map( d3.random.normal() ),
    data = [ { x:x, y:y1, type:'scatter', name:'Trial 1',
        mode:'markers', marker:{size:16} },
        { x:x, y:y2, type:'scatter', name:'Trial 2',
        mode:'markers', marker:{size:16} } ];
    layout = { 
        hovermode:'closest',
        title:'Hover on Points'
     };

Plotly.plot('theDiv', data, layout, {showSendToCloud: true});

myPlot.on('plotly_hover', function(data){
    var infotext = data.points.map(function(d){
      return (d.data.name+': x= '+d.x+', y= '+d.y.toPrecision(3));
    });
  
    hoverInfo.innerHTML = infotext.join('<br/>');
})
 .on('plotly_unhover', function(data){
    hoverInfo.innerHTML = '';
});

</script>

